Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2014-05-13 CGP Journal/main.tex
Updated URL to be correct.
Renamed files to match IEEE requirements

To prevent undue biasing in the final results, these tuning runs were
not used in the subsequent data analysis.  Effectively, the runs used to set
the parameter configuration were considered
the training runs for that configuration.  As a result, our final results were gathered
from a completely independent set of runs to test the configuration's general characteristics.
Each configuration was run 50 times to ensure statistical power.  All told over
11.5 billion evaluations were performed to gather our results.  The source code
used to produce our results is available from our website.\footnote{\url{https://website.name.removed.com/AnonymousCGP}}

@@

\begin{table*}
	\caption{Location of never active nodes across all 50 runs for all nine algorithm combinations on the Multiply problem.}
	\centering
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{multiply_skip_normal} &
                        \graphicthird{multiply_skip_reorder} &
                        \graphicthird{multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{multiply_accumulate_normal} &
                              \graphicthird{multiply_accumulate_reorder} &
                              \graphicthird{multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{multiply_single_normal} &
                          \graphicthird{multiply_single_reorder} &
                          \graphicthird{multiply_single_dag}\\ \hline
	\end{tabular}
	\label{tab:never_active}
\end{table*}

@@

\begin{table*}
	\centering
	\caption{Average node behavior for all nine algorithm combinations on the Encode problem.
	         Excludes never active nodes.}
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{bar_encode_skip_normal} &
                        \graphicthird{bar_encode_skip_reorder} &
                        \graphicthird{bar_encode_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{bar_encode_accumulate_normal} &
                              \graphicthird{bar_encode_accumulate_reorder} &
                              \graphicthird{bar_encode_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{bar_encode_single_normal} &
                          \graphicthird{bar_encode_single_reorder} &
                          \graphicthird{bar_encode_single_dag}\\ \hline
	\end{tabular}
	\label{tab:encode_behavior}
\end{table*}

\begin{table*}
	\centering
	\caption{Average node behavior for all nine algorithm combinations on the Multiply problem.
	         Excludes never active nodes.}
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{bar_multiply_skip_normal} &
                        \graphicthird{bar_multiply_skip_reorder} &
                        \graphicthird{bar_multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{bar_multiply_accumulate_normal} &
                              \graphicthird{bar_multiply_accumulate_reorder} &
                              \graphicthird{bar_multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{bar_multiply_single_normal} &
                          \graphicthird{bar_multiply_single_reorder} &
                          \graphicthird{bar_multiply_single_dag}\\ \hline
	\end{tabular}
	\label{tab:multiply_behavior}
\end{table*}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{goldman_headshot}}]{Brian W. Goldman}
received the B. S. degree and M.S. degree in computer science from the
Missouri University of Science and Technology, Rolla, in 2010
and 2012 respectively.

@@

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{headPunch}}]{William F. Punch}
Bill Punch received his Ph.D. from the Ohio State University and is currently an
Associate Professor at the Computer Science and Engineering Department of Michigan
State University. He is also the  director of the MSU High Performance Computing
Center. His research interests are evolutionary computation, high performance
computing and computing pedagogy. He co-directs the Genetic Algorithms Research
and Application Group (GARAGe) and is on the executive committee of the NSF STC,
BEACON, at MSU. His book with Rich Enbody titled "The Practice of Computing Using
Python" is now in its second edition.
\end{IEEEbiography}

>>>>

To prevent undue biasing in the final results, these tuning runs were
not used in the subsequent data analysis.  Effectively, the runs used to set
the parameter configuration were considered
the training runs for that configuration.  As a result, our final results were gathered
from a completely independent set of runs to test the configuration's general characteristics.
Each configuration was run 50 times to ensure statistical power.  All told over
11.5 billion evaluations were performed to gather our results.  The source code
used to produce our results is available from our
website.\footnote{\url{https://github.com/brianwgoldman/Analysis-of-CGPs-Mechanisms}}

@@

\begin{table*}
	\caption{Location of never active nodes across all 50 runs for all nine algorithm combinations on the Multiply problem.}
	\centering
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{goldm00_multiply_skip_normal} &
                        \graphicthird{goldm01_multiply_skip_reorder} &
                        \graphicthird{goldm02_multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{goldm03_multiply_accumulate_normal} &
                              \graphicthird{goldm04_multiply_accumulate_reorder} &
                              \graphicthird{goldm05_multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{goldm06_multiply_single_normal} &
                          \graphicthird{goldm07_multiply_single_reorder} &
                          \graphicthird{goldm08_multiply_single_dag}\\ \hline
	\end{tabular}
	\label{tab:never_active}
\end{table*}

@@

\begin{table*}
	\centering
	\caption{Average node behavior for all nine algorithm combinations on the Encode problem.
	         Excludes never active nodes.}
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{goldm09_bar_encode_skip_normal} &
                        \graphicthird{goldm10_bar_encode_skip_reorder} &
                        \graphicthird{goldm11_bar_encode_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{goldm12_bar_encode_accumulate_normal} &
                              \graphicthird{goldm13_bar_encode_accumulate_reorder} &
                              \graphicthird{goldm14_bar_encode_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{goldm15_bar_encode_single_normal} &
                          \graphicthird{goldm16_bar_encode_single_reorder} &
                          \graphicthird{goldm17_bar_encode_single_dag}\\ \hline
	\end{tabular}
	\label{tab:encode_behavior}
\end{table*}

\begin{table*}
	\centering
	\caption{Average node behavior for all nine algorithm combinations on the Multiply problem.
	         Excludes never active nodes.}
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{goldm18_bar_multiply_skip_normal} &
                        \graphicthird{goldm19_bar_multiply_skip_reorder} &
                        \graphicthird{goldm20_bar_multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{goldm21_bar_multiply_accumulate_normal} &
                              \graphicthird{goldm22_bar_multiply_accumulate_reorder} &
                              \graphicthird{goldm23_bar_multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{goldm24_bar_multiply_single_normal} &
                          \graphicthird{goldm25_bar_multiply_single_reorder} &
                          \graphicthird{goldm26_bar_multiply_single_dag}\\ \hline
	\end{tabular}
	\label{tab:multiply_behavior}
\end{table*}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{goldm27_goldman_headshot}}]{Brian W. Goldman}
received the B. S. degree and M.S. degree in computer science from the
Missouri University of Science and Technology, Rolla, in 2010
and 2012 respectively.

@@

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{goldm28_headPunch}}]{William F. Punch}
Bill Punch received his Ph.D. from the Ohio State University and is currently an
Associate Professor at the Computer Science and Engineering Department of Michigan
State University. He is also the  director of the MSU High Performance Computing
Center. His research interests are evolutionary computation, high performance
computing and computing pedagogy. He co-directs the Genetic Algorithms Research
and Application Group (GARAGe) and is on the executive committee of the NSF STC,
BEACON, at MSU. His book with Rich Enbody titled "The Practice of Computing Using
Python" is now in its second edition.
\end{IEEEbiography}
